Designing Turk Experiments for Visual Statistical Inference

### 2013-06-22 paper_turk.tex
last review before submission

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{plot_turk2_100_450_12_3.png} 
   \caption{A lineup of 20 scatter plots with least square line overlaid. Which of these plots shows the steepest slope?.}
   \label{fig:lineup_turk}
\end{figure}

@@

\item The number of worker to recruit has to be provided so that the turk task is live until specific number of people do the task. This is related to the sample size we intend to collect on each lineup.

\item Time allowed to finish each task has to be specified. Once a specific time period is set up the task will be expired after that time and the worker can't be submit it anymore. The worker has to finish the task by that time period.

@@

\item Duration of the task is the period of time the task is available for workers to do. If the time period is over the task will not be available no matter whether all the required number of workers have participated or not. This duration is important as each payment has to be finalized by this time period. Otherwise, all the workers will be paid automatically after this time period no matter if the the task is accepted or rejected. Some times it is helpful to set up a longer duration and see how long it takes before all the tasks get completed.

@@

\subsection{Accepting or Rejecting the Task} There is no hard and fast rule to follow while accepting or rejecting the tasks submitted by the MTurk workers. Since MTurk task are very simple and payment amount is very small the general convention is to pay every worker who submitted the task properly as instructed. The task should not be rejected based on the quality of work unless it prominently demonstrates that the task was not performed properly and irrelevant or garbage data were provided. It is very unusual to get garbage data from MTurk workers since they are well aware that this conduct may harm their reputation as a worker. So, proper caution needs to be taken while rejecting a task. Some times may happen that the workers provided crap data unintentionally. In that case we recommend to accept the task and pay for trying the task.

@@

Other criteria to accept or reject the tasks may be more complex based on the experimental needs. For example one may accept the task if certain percentage of the easy lineups are correctly evaluated. This criteria can be used if multiple number of easy lineups are shown for evaluation. For example if there are 3 easy lineups and none of them were correctly evaluated it is most likely that the feedbacks were provided randomly. Some times it may happen that out of 10 lineups 3 were correctly evaluated but all the three easy lineups were wrongly evaluated. In that case the payment should be made since it is very unlikely that out of 10 lineups a total of 3 lineups would be correctly evaluated by just random response.
%These issues would be addressed in our future work based on the several turk experiments that we intend to carry out.

@@

\subsection{Managing Worker} Accepting the task and processing the payment in a timely manner may make a good impression for the task they just did. This is helpful for the recruiter's reputation so that in future the recruiter can get the job done faster. Since the MTurk worker will always  prefer the tasks posted by a good recruiter. Besides this we provide some good worker management strategy as below.

@@

The duration of an experiment to finish depends on the time it was posted and the number of interested workers available on that time. It also depends on how attractive the experiment is in terms of appearance and payment. Even though the payment was similar for all the experiments, ee observed some experiments were finished much faster than others. Experiment 8 took long time to finish which is about 77 hours for 100 tasks while experiment 7 took only 4.86 hours to finish 100 task.

@@

While selection bias may influence the results of some experimental study it is not much of an issue for experiment with lineups. In terms of demographic factors and geographic location MTurk provides much diversity in the participants as we see in \cite{majumder:socio}. Moreover it is observed that the human factors do not have any practical impact on the probability of correctly identifying the data plot in the lineup.

@@

\section{Conclusion} This paper presents a complete solution to the problem of designing a simulation experiment for lineup and recruiting people to get the lineups evaluated. The online application design provides features to control how the multiple lineups can be presented to an observer. Scalable Vector Graphics (SVG) are used for lineup so that observer can click on the lineup to pick certain plot. This also made the multiple plot selection from a lineup easier and convenient. Multiple online experiments are done using this web application and result suggests that the application worked as planned.

@@

We also intend to set up a web application for public use where researcher can put their lineup for online evaluation. The observer can be recruited from MTurk or any other source including local lab participants.

>>>>

\begin{figure}[htbp] 
   \centering
   \includegraphics[width=6.5in]{plot_turk2_100_450_12_3.png} 
   \caption{A lineup of 20 scatter plots with least square line overlaid. Which of these plots shows the steepest slope? Answer to this question can be found at the end of conclusion.}
   \label{fig:lineup_turk}
\end{figure}

@@

\item The number of worker to recruit has to be provided so that the turk task remain open until specific number of people do the task. This is related to the sample size of the data we intend to collect on each lineup.

\item Time allowed to finish each task has to be specified. Once a specific time period is set up the task will be expired after that time and the worker can't submit it anymore. The worker has to finish the task by that time period once he or she agrees to do the task.

@@

\item Duration of the task is the period of time the task is available for workers to do. If the time period is over the task will not be available no matter whether all the required number of workers have participated or not. This duration is important as each payment has to be finalized by this time period. Otherwise, all the workers will be paid automatically after this time period no matter whether the the task is accepted or rejected. Some times it is helpful to set up a longer duration and see how long it takes before all the tasks get completed.

@@

\subsection{Accepting or Rejecting the Task} There is no hard and fast rule to follow while accepting or rejecting the tasks submitted by the MTurk workers. Since MTurk task are very simple and payment amount is very small the general convention is to pay every worker who submitted the task properly as instructed. The task should not be rejected based on the quality of work unless it clearly demonstrates that the task was not performed properly and irrelevant or garbage data were provided. It is very unusual to get garbage data from MTurk workers since they are well aware that this conduct may harm their reputation as a worker. So, proper caution needs to be taken while rejecting a task. Some times it may happen that the workers provided invalid data unintentionally. In that case we recommend to accept the task and pay for trying the task.

@@

Other criteria to accept or reject the tasks may be more complex based on the experimental needs. For example one may accept the task if certain percentage of the easy lineups are correctly evaluated. This criteria can be used if multiple number of easy lineups are shown for evaluation. For example if there are 3 easy lineups and none of them were correctly evaluated it is most likely that the feedbacks were provided randomly. Some times it may happen that out of 10 lineups 3 difficult lineups were correctly evaluated but all the three easy lineups were wrongly evaluated. In that case the payment should be made since it is very unlikely that out of 10 lineups a total of 3 lineups would be correctly evaluated by just random response.
%These issues would be addressed in our future work based on the several turk experiments that we intend to carry out.

@@

\subsection{Managing Worker} Accepting the task and processing the payment in a timely manner may make a good impression about the task and the recruiter. This is helpful for the recruiter's reputation so that in future the recruiter can get the job done faster. Since the MTurk worker will always  prefer the tasks posted by a good recruiter. Besides this we provide some good worker management strategy as below.

@@

The duration of an experiment to finish depends on the time it was posted and the number of interested workers available on that time. It also depends on how attractive the experiment is in terms of appearance and payment. Even though the payment was similar for all the experiments, we observed some experiments were finished much faster than others. Experiment 8 took long time to finish which is about 77 hours for 100 tasks while experiment 7 took only 4.86 hours to finish 100 task.

@@

While selection bias may influence the results of some experimental study it is not much of an issue for experiment with lineups. In terms of demographic factors and geographic location MTurk provides much diversity in the participants as studied by \cite{majumder:socio}. Moreover it is observed that the human factors do not have any practical impact on the probability of correctly identifying the data plot in the lineup.

@@

\section{Conclusion} This paper presents a complete solution to the problem of designing a simulation experiment for lineup and recruiting people to get the lineups evaluated. The online application design provides features to control how the multiple lineups can be presented to an observer. Scalable Vector Graphics (SVG) are used for lineup so that observer can click on the lineup to pick certain plot. This also made the multiple plot selection from a lineup easier and convenient. The web site is used for multiple online experiments.

@@

We also intend to set up a web application for public use where researcher can put their lineup for online evaluation. The observer can be recruited from MTurk or any other sources including local lab participants.

\paragraph{Answer to the question in Figure~\ref{fig:lineup_turk} is 2.}
